Age-related changes in plant growth and traits

### 2016-10-05 scripts/Accessory_figs_20160905.Rmd
creating 3D plot of leaf replacement, new leaf, and reproductive investment

plot(scaled_ovule_count ~ prepollen_costs, SummarySpp[["mean"]],log="xy",pch=1,col=col.spp(species),xlab="cost to make a unit: dashed =ovule; solid=seed",ylim=c(.001,200),ylab="scaled count",xlim=c(.01,100),cex=1.5)
points(scaled_seed_count ~ embryo_endo_size, SummarySpp[["mean"]],cex=1.5,pch=16,col=col.spp(species))
line_function_log_xy(SummarySpp[["mean"]]$prepollen_costs,mod1,3)
line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod2,1)
#points(scaled_seed_count ~ seed_costs, SummarySpp[["mean"]],pch=12,col=col.spp(species))
arrows(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$scaled_seed_count,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["mean"]]$scaled_ovule_count,col=col.spp(SummarySpp[["mean"]]$species),code=1,length=.15)

>>>>

plot(scaled_ovule_count ~ prepollen_costs, SummarySpp[["mean"]],log="xy",pch=1,col=col.spp(species),xlab="cost to make a unit: dashed =ovule; solid=seed",ylim=c(.001,200),ylab="scaled count",xlim=c(.01,100),cex=1.5)
points(scaled_seed_count ~ embryo_endo_size, SummarySpp[["mean"]],cex=1.5,pch=16,col=col.spp(species))
line_function_log_xy(SummarySpp[["mean"]]$prepollen_costs,mod1,3)
line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod2,1)
#points(scaled_seed_count ~ seed_costs, SummarySpp[["mean"]],pch=12,col=col.spp(species))
arrows(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$scaled_seed_count,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["mean"]]$scaled_ovule_count,col=col.spp(SummarySpp[["mean"]]$species),code=0,length=.15)

### 2016-10-05 scripts/RA_figs_20160627.Rmd
creating 3D plot of leaf replacement, new leaf, and reproductive investment

#Figure 1 Different species have different RA values. But biggest shift in RA is with age
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7.5}
if (min(SummaryInd$growth_leaf) <= 0) {
  SummaryInd$growth_leaf_positive = SummaryInd$growth_leaf - SummaryInd$growth_leaf_min + 1
} else {
  SummaryInd$growth_leaf_positive = SummaryInd$growth_leaf
}

@@

#pdf("figs2/RA/Figure_1_leaf_vs_repro.pdf", height=4.3, width=8)
win.metafile("figs2/RA/Figure_1_leaf_vs_repro.wmf", height=4.3, width=8)
plot
par(mfrow=c(1,2), cex=1, omi=c(1.1,0.8,.1,.1), mai=c(0.3,.4,.1,0.2)) 
plot(repro_inv~growth_leaf_positive, subset(SummaryInd,growth_leaf_positive>1), log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),
     xlab="",ylab="",yaxt="n",xaxt="n",cex=0.8)
axis(1, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
axis(2, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.6,bty="n")
abline(0,1)
text(10^5.6,10^5.8,srt=45,"RA = 0.5",cex=.6)
abline(log10(3),1)
text(10^5.13,10^5.8,srt=45,"RA = 0.75",cex=.6)
abline(log10(9),1)
text(10^4.67,10^5.8,srt=45,"RA = 0.9",cex=.6)
abline(log10(19),1)
text(10^4.33,10^5.8,srt=45,"RA = 0.95",cex=.6)
abline(log10(.111),1)
text(10^5.6,10^4.85,srt=45,"RA = 0.1",cex=.6)
abline(log10(.010101),1)
text(10^5.6,10^3.8,srt=45,"RA = 0.01",cex=.6)
mtext("reproductive investment (mg)",2,line=1,outer=TRUE)

@@

scatterplot3d(SummaryInd$leaf_shed,SummaryInd$leaf_inv_gross,SummaryInd$repro_inv,log="xyz",color=col.spp(SummaryInd$species),pch=16)
```

#Figure 1 - alternate rendition, not scaling leaf investment to be positive
```{r}
pdf("figs2/RA/Figure_1_alt_leaf_vs_repro.pdf", height=4.3, width=8)
plot

@@

plot(repro_inv~jitter(growth_leaf_no_neg_values), subset(SummaryInd), log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),
     xlab="",ylab="",cex=0.8,xaxt="n",yaxt="n")
axis(1, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
axis(2, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
#legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.6,bty="n")
abline(0,1)
text(10^5.6,10^5.8,srt=45,"RA = 0.5",cex=.6)
abline(log10(3),1)
text(10^5.13,10^5.8,srt=45,"RA = 0.75",cex=.6)
abline(log10(9),1)
text(10^4.67,10^5.8,srt=45,"RA = 0.9",cex=.6)
abline(log10(19),1)
text(10^4.33,10^5.8,srt=45,"RA = 0.95",cex=.6)
abline(log10(.111),1)
text(10^5.6,10^4.85,srt=45,"RA = 0.1",cex=.6)
abline(log10(.010101),1)
text(10^5.6,10^3.8,srt=45,"RA = 0.01",cex=.6)
mtext("reproductive investment (mg)",2,line=1,outer=TRUE)

plot(repro_inv~growth_leaf_no_neg_values, subset(SummaryInd), log="xy", col=col.age(age),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),
     xlab="",ylab="",cex=0.8,xaxt="n",yaxt="n")
axis(1, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
axis(2, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
#legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.6,bty="n")
abline(0,1)
text(10^5.6,10^5.8,srt=45,"RA = 0.5",cex=.6)
abline(log10(3),1)
text(10^5.13,10^5.8,srt=45,"RA = 0.75",cex=.6)
abline(log10(9),1)
text(10^4.67,10^5.8,srt=45,"RA = 0.9",cex=.6)
abline(log10(19),1)
text(10^4.33,10^5.8,srt=45,"RA = 0.95",cex=.6)
abline(log10(.111),1)
text(10^5.6,10^4.85,srt=45,"RA = 0.1",cex=.6)
abline(log10(.010101),1)
text(10^5.6,10^3.8,srt=45,"RA = 0.01",cex=.6)

@@

@@

for(spp in names(data)) {
  plot(RA_leaf_area~age,data2[[spp]],col=col.age(data2[[spp]]$age),pch=16,xlab="",ylab="",log="x",xlim=c(1,40),ylim=c(-0.25,1.75),yaxt="n",xaxt="n")
  points(RA_leaf_area~age,data[[spp]],pch=151,col=col.age(data[[spp]]$age),cex=1.5)
   if(spp=="BOLE"|spp=="COER") {
    rect(14,par("usr")[3],10^par("usr")[2],par("usr")[4],col="light grey",density=NA)
    rect(10^par("usr")[1],par("usr")[3],10^par("usr")[2],par("usr")[4],col="black",density=0)
  }
    if(spp=="GRSP"|spp=="HEPU") {
    rect(20,par("usr")[3],10^par("usr")[2],par("usr")[4],col="light grey",density=NA)
    rect(10^par("usr")[1],par("usr")[3],10^par("usr")[2],par("usr")[4],col="black",density=0)
  }
  if(spp=="PILI") {
    rect(10,par("usr")[3],10^par("usr")[2],par("usr")[4],col="light grey",density=NA)
    rect(10^par("usr")[1],par("usr")[3],10^par("usr")[2],par("usr")[4],col="black",density=0)
  }
  abline(0,0)
  abline(1,0,lty=3)
  axis(1, at=c(1,2,5,10,20,30), labels=c("","","","","",""),cex.axis=.8,las=1,tck=-.03) 
  axis(2, at=c(-0,0.5,1,1.5), labels=c("","","",""),cex.axis=.8,las=1,tck=-.03)

  if(spp=="GRBU"|spp=="PELA"|spp=="PUTU"){
    axis(1, at=c(1,2,5,10,20,30), labels=c(1,2,5,10,20,30),cex.axis=.8,las=1) 
      } else{}
  if(spp=="BAER"|spp=="BOLE"|spp=="COER"|spp=="EPMI"|spp=="GRBU"){
    axis(2, at=c(-0,0.5,1,1.5), labels=c(-0,0.5,1,1.5),cex.axis=.8,las=1)
  } else{}
  extra.top.left.logx(labels.spp.full(spp),3)
  extra.bottom.left.logx(data3[[spp]]$RA_type,1)
}

>>>>

###playing with variables to try and show meaningful RA plots despite negative leaf growth values
``` {r}
if (min(SummaryInd$growth_leaf) <= 0) {
  SummaryInd$growth_leaf_positive = SummaryInd$growth_leaf - SummaryInd$growth_leaf_min + 1
} else {
  SummaryInd$growth_leaf_positive = SummaryInd$growth_leaf
}

@@

SummaryInd$growth_leaf_fixed_max = SummaryInd$growth_leaf
SummaryInd$RA_fixed_max = SummaryInd$RA_leaf_area
for (i in 1:length(SummaryInd$individual)) {
  if (SummaryInd$RA_leaf_area[i] < 0) {
  SummaryInd$growth_leaf_fixed_max[i] = SummaryInd$repro_inv[i]*0.005
  SummaryInd$RA_fixed_max[i] = 1.1 
  }
   if (SummaryInd$RA_leaf_area[i] > 1) {
  SummaryInd$growth_leaf_fixed_max[i] = SummaryInd$repro_inv[i]*0.005
  SummaryInd$RA_fixed_max[i] = 1.1
  }
}

SummaryInd$leaf_replacement = SummaryInd$growth_leaf
SummaryInd$leaf_new = SummaryInd$growth_leaf
SummaryInd$leaf_new_nonzero = SummaryInd$growth_leaf
for (i in 1:length(SummaryInd$individual)) {
  if (SummaryInd$growth_leaf[i] < 0) {
  SummaryInd$leaf_replacement[i] = SummaryInd$leaf_inv_gross[i]
  SummaryInd$leaf_new_nonzero[i] =.1
  SummaryInd$leaf_new[i] = 0
  }
   if (SummaryInd$growth_leaf[i] > 0) {
  SummaryInd$leaf_replacement[i] = SummaryInd$leaf_shed[i]
  SummaryInd$leaf_new[i] = SummaryInd$growth_leaf[i]
  SummaryInd$leaf_new_nonzero[i] =SummaryInd$growth_leaf[i]
  }
}

SummaryInd$repro_inv_nonzero = SummaryInd$repro_inv
for (i in 1:length(SummaryInd$individual)) {
  if (SummaryInd$repro_inv[i] < .0001) {
    SummaryInd$repro_inv_nonzero[i] = .1
  }
}

plot(leaf_replacement~leaf_new, subset(SummaryInd), log="xy", col=col.spp(species),pch=16)
abline(0,1)

plot(leaf_replacement~leaf_new, subset(SummaryInd), log="xy", col=col.age(age),pch=16)
abline(0,1)

scatterplot3d(log(SummaryInd$repro_inv_nonzero),log(SummaryInd$leaf_new_nonzero),log(SummaryInd$leaf_replacement),color=col.spp(SummaryInd$species),pch=16,type="h",lty.hplot=3)

scatterplot3d(log(SummaryInd$leaf_replacement),log(SummaryInd$leaf_new),log(SummaryInd$repro_inv),color=col.spp(SummaryInd$species),pch=16,type="h", lty.hplot=3)

scatterplot3d(log10(SummaryInd$leaf_replacement),log10(SummaryInd$leaf_new),log10(SummaryInd$repro_inv_nonzero),color=col.spp(SummaryInd$species),pch=16,grid=TRUE,type="h", lty.hplot=3,lwd=.2,xlim=c(-1,6),ylim=c(-1,6),zlim=c(-1,6))

planes3d(0, x.coef = 1, y.coef = 1, lty = "dashed",)

par(mfrow=c(1,1), cex=1, omi=c(1.1,0.8,.1,.1), mai=c(0.3,.4,.1,0.2)) 
```

#Figure 1 Different species have different RA values. But biggest shift in RA is with age
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7.5}
#pdf("figs2/RA/Figure_1_leaf_vs_repro.pdf", height=4.3, width=8)
win.metafile("figs2/RA/Figure_1_leaf_vs_repro.wmf", height=4.3, width=8)
plot
par(mfrow=c(1,2), cex=1, omi=c(1.1,0.8,.1,.1), mai=c(0.3,.4,.1,0.2)) 
plot(repro_inv~growth_leaf_positive, subset(SummaryInd,growth_leaf_positive>1), log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),
     xlab="",ylab="",yaxt="n",xaxt="n",cex=0.8)
axis(1, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
axis(2, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.6,bty="n")
abline(0,1)
text(10^5.6,10^5.8,srt=45,"RA = 0.5",cex=.6)
abline(log10(3),1)
text(10^5.13,10^5.8,srt=45,"RA = 0.75",cex=.6)
abline(log10(9),1)
text(10^4.67,10^5.8,srt=45,"RA = 0.9",cex=.6)
abline(log10(19),1)
text(10^4.33,10^5.8,srt=45,"RA = 0.95",cex=.6)
abline(log10(.111),1)
text(10^5.6,10^4.85,srt=45,"RA = 0.1",cex=.6)
abline(log10(.010101),1)
text(10^5.6,10^3.8,srt=45,"RA = 0.01",cex=.6)
mtext("reproductive investment (mg)",2,line=1,outer=TRUE)

@@

scatterplot3d(SummaryInd$leaf_shed,SummaryInd$leaf_inv_gross,SummaryInd$repro_inv,log="xyz",color=col.spp(SummaryInd$species),pch=16)

ternary <- dplyr::select(SummaryInd,species,age,leaf_shed,growth_leaf,pack_disp_costs,seed_costs,embryo_endo_size)
ternary$per_poll <-100*ternary$prepollen_costs/ternary$seed_costs
ternary$post_poll <- 100-ternary$per_poll
ternary$per_seed <-100*ternary$embryo_endo_size/ternary$seed_costs
ternary$per_disp <-100*ternary$pack_disp_costs/ternary$seed_costs

mod_poll <- sma(per_poll~seed_costs,ternary,slope.test=0,method="OLS",log="x")
mod_seed <- sma(per_seed~seed_costs,ternary,slope.test=0,method="OLS",log="x")
mod_disp <- sma(per_disp~seed_costs,ternary,slope.test=0,method="OLS",log="x")
mod_post_poll <- sma(post_poll~seed_costs,ternary,slope.test=0,method="OLS",log="x")

costs_per_seed <- as.data.frame("costs for seed (%)")
costs_per_seed <- cbind(costs_per_seed,dplyr::select(mod_seed$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
names(costs_per_seed) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")

costs_per_seed2 <- as.data.frame("costs for pre-pollination (%)")
costs_per_seed2 <- cbind(costs_per_seed2,dplyr::select(mod_poll$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
names(costs_per_seed2) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
costs_per_seed <- rbind(costs_per_seed,costs_per_seed2)

costs_per_seed2 <- as.data.frame("costs for dispersal (%)")
costs_per_seed2 <- cbind(costs_per_seed2,dplyr::select(mod_disp$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
names(costs_per_seed2) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
costs_per_seed <- rbind(costs_per_seed,costs_per_seed2)

write.csv(costs_per_seed, file="figs2/Accessory_Costs/Table00_in_text_costs_per_seed.csv",row.names=FALSE)

win.metafile("figs2/Accessory_Costs/FigureXX_seedcost_components.wmf", height=6, width=6)
plot

plot(per_seed~seed_costs,ternary,col="black",log="x",pch=21,cex=2,ylim=c(0,75),ylab="prop of seed_costs")
points(per_poll~seed_costs,ternary,col="red",pch=16,cex=2)
points(per_disp~seed_costs,ternary,col="blue",pch=16,cex=2)

abline(mod_poll$groupsummary["Int"][[1]],mod_poll$groupsummary["Slope"][[1]],col="red",lwd=2)
abline(mod_seed$groupsummary["Int"][[1]],mod_seed$groupsummary["Slope"][[1]],col="black",lty=2,lwd=2)
abline(mod_disp$groupsummary["Int"][[1]],mod_disp$groupsummary["Slope"][[1]],col="blue",lwd=2)
legend("topright",legend=c("seed","prepollen","pack&disp"),col=c("black","red","blue"),pch=16, cex=1.1,bty="n")
v <- sqrt(ternary$seed_costs/500)
ternary$horz <- c(1.8,1.3,1.2,-0.3,0.6,0.6,0.5,-0.2,1.3,1.7,1.4,-0.2,-0.3,-0.3)
ternary$vert <- c(v[1]*-1.7,v[2]*1.1,v[3]*1.2,v[4],v[5]*-2.3,v[6]*4.5,v[7],v[8]*1.6,v[9],v[10]*0.2,v[11],v[12],v[13],v[14])
ternary = ternary[with(ternary, order(-seed_costs)), ]
label <- 20

dev.off()
library(ggtern)
win.metafile("figs2/Accessory_Costs/Figure03_ternary_diagram_seed_costs.wmf", height=5, width=5)
plot

par(mfrow=c(1,1), cex=1, omi=c(2,2,2,2), mai=c(2,2,2,2))

ggtern(data=ternary,aes(y=per_seed,x=per_poll,z=per_disp)) +
      geom_point(size=sqrt(ternary$seed_costs/2),shape=20,color=col.spp(ternary$species)) +
      theme_bw() + 
      theme_showarrows() +
      geom_text(label=ternary$species, color="black", hjust=ternary$horz, 
                 vjust=ternary$vert,size=2) +
      ggtitle("Seed cost components")+
      labs(T="embryo+endosperm",L="pre-pollination",R="provisioning")+
      Tarrowlab("embryo + endosperm weight (%)")+
      Larrowlab("pre-pollination costs (%)")+
      Rarrowlab("provisioning costs (%)")+
      theme(plot.title = element_text(size=11,face="bold"))+
      theme(tern.axis.title.T = element_text(size=9,face="plain"))+
      theme(tern.axis.title.L = element_text(size=9,face="plain",hjust=0,vjust=1.7))+
      theme(tern.axis.title.R = element_text(size=9,face="plain",hjust=1,vjust=1.7))+
      theme(tern.axis.arrow.text = element_text(size=9,face="plain"))+
      theme(tern.axis.arrow.start= 0.2)+ 
      theme(tern.axis.arrow.finish=0.8)

```

#Figure 1 - alternate rendition, not scaling leaf investment to be positive, reassigning "negative" leaf investment individuals to RA =1.1
```{r}
pdf("figs2/RA/Figure_1_alt_leaf_vs_repro.pdf", height=4.3, width=8)
plot

@@

plot(repro_inv~(growth_leaf_fixed_max), subset(SummaryInd), log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),
     xlab="",ylab="",cex=0.8,xaxt="n",yaxt="n")
axis(1, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
axis(2, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
#legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.6,bty="n")
abline(0,1)
text(10^5.6,10^5.8,srt=45,"RA = 0.5",cex=.6)
abline(log10(3),1)
text(10^5.13,10^5.8,srt=45,"RA = 0.75",cex=.6)
abline(log10(9),1)
text(10^4.67,10^5.8,srt=45,"RA = 0.9",cex=.6)
abline(log10(19),1)
text(10^4.33,10^5.8,srt=45,"RA = 0.95",cex=.6)
abline(log10(.111),1)
text(10^5.6,10^4.85,srt=45,"RA = 0.1",cex=.6)
abline(log10(.010101),1)
text(10^5.6,10^3.8,srt=45,"RA = 0.01",cex=.6)
mtext("reproductive investment (mg)",2,line=1,outer=TRUE)

plot(repro_inv~growth_leaf_fixed_max, subset(SummaryInd), log="xy", col=col.age(age),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),
     xlab="",ylab="",cex=0.8,xaxt="n",yaxt="n")
axis(1, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
axis(2, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
#legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.6,bty="n")
abline(0,1)
text(10^5.6,10^5.8,srt=45,"RA = 0.5",cex=.6)
abline(log10(3),1)
text(10^5.13,10^5.8,srt=45,"RA = 0.75",cex=.6)
abline(log10(9),1)
text(10^4.67,10^5.8,srt=45,"RA = 0.9",cex=.6)
abline(log10(19),1)
text(10^4.33,10^5.8,srt=45,"RA = 0.95",cex=.6)
abline(log10(.111),1)
text(10^5.6,10^4.85,srt=45,"RA = 0.1",cex=.6)
abline(log10(.010101),1)
text(10^5.6,10^3.8,srt=45,"RA = 0.01",cex=.6)

@@

#data2 <- subset(SummaryInd,RA_leaf_area>-2&RA_leaf_area<3)
data2 <- subset(SummaryInd)
data2 <- split(data2, data2$species)

@@

for(spp in names(data)) {
  plot(RA_fixed_max~age,data2[[spp]],col=col.age(data2[[spp]]$age),pch=16,xlab="",ylab="",log="x",xlim=c(1,40),ylim=c(-0.25,1.75),yaxt="n",xaxt="n")
  points(RA_leaf_area~age,data[[spp]],pch=151,col=col.age(data[[spp]]$age),cex=1.5)
   if(spp=="BOLE"|spp=="COER") {
    rect(14,par("usr")[3],10^par("usr")[2],par("usr")[4],col="light grey",density=NA)
    rect(10^par("usr")[1],par("usr")[3],10^par("usr")[2],par("usr")[4],col="black",density=0)
  }
    if(spp=="GRSP"|spp=="HEPU") {
    rect(20,par("usr")[3],10^par("usr")[2],par("usr")[4],col="light grey",density=NA)
    rect(10^par("usr")[1],par("usr")[3],10^par("usr")[2],par("usr")[4],col="black",density=0)
  }
  if(spp=="PILI") {
    rect(10,par("usr")[3],10^par("usr")[2],par("usr")[4],col="light grey",density=NA)
    rect(10^par("usr")[1],par("usr")[3],10^par("usr")[2],par("usr")[4],col="black",density=0)
  }
  abline(0,0)
  abline(1,0,lty=3)
  axis(1, at=c(1,2,5,10,20,30), labels=c("","","","","",""),cex.axis=.8,las=1,tck=-.03) 
  axis(2, at=c(-0,0.5,1,1.5), labels=c("","","",""),cex.axis=.8,las=1,tck=-.03)

  if(spp=="GRBU"|spp=="PELA"|spp=="PUTU"){
    axis(1, at=c(1,2,5,10,20,30), labels=c(1,2,5,10,20,30),cex.axis=.8,las=1) 
      } else{}
  if(spp=="BAER"|spp=="BOLE"|spp=="COER"|spp=="EPMI"|spp=="GRBU"){
    axis(2, at=c(-0,0.5,1,1.5), labels=c(-0,0.5,1,1.5),cex.axis=.8,las=1)
  } else{}
  extra.top.left.logx(labels.spp.full(spp),3)
  extra.bottom.left.logx(data3[[spp]]$RA_type,1,0.8)
}
